\acknowledgements
%\setstretch{1.75}
%
I want to convey my deepest gratitude to my supervisor, Prof. Mahesh Kumar for his unwavering support, direction, and inspiration throughout my research journey. I am truly grateful for the freedom he provided me to explore different technologies and become an independent researcher. I consider myself fortunate to have had the opportunity to work with him and to have access to his well established laboratory.  

I extend my thanks to my doctoral committee members, Prof. K. Shanti Swarup, Prof. B. Kalyan Kumar, Prof. Srirama Srinivas, and Prof. Mallikarjuna J., for their critical evaluation of my work and valuable suggestions.
I would like to acknowledge Prof. Nagendra Krishnapura, Prof. Ravinder David Koilpillai, and Prof. Devendra Jalihal, who served as the Heads of the Department during my research period. 

I am grateful to the Indian Institute of Technology Madras for providing me with the necessary academic and technical resources to successfully complete my research. I also want to express my gratitude to the Ministry of Human Resource Development, India, for their financial support during my Ph.D. at IIT Madras.

I would like to thank my fellow researchers, Dr. Srikanth Kotra, Dr. Satish R., Mr. Nafih M., Mr. Pruthvi Chaitanya N., Dr. Hariharan R., Mr. Durga Malleswara Rao, Mr. Manik Pradhan, Mr. Leela Krishna,  Mr. Rajarshi B., Mr. Rohan M., Ms. Leelavathi, Mr. Abhishek Panda, Mr. Tony Thomas, Mrs. Nimitha, Dr. Surendra, Mr. Sudheer, Mr. Vardhan Varma, and Mr. Upendran, for their cooperation and assistance throughout my research work and lab responsibilities. I also thank Mr. Harish and Mr. Malakonda Reddy for making my stay joyful and pleasant.

Finally, I want to thank my parents and sisters for their unwavering support in pursuing my higher studies. I am thankful to all those who have directly or indirectly contributed to the successful completion of this thesis.  

\begin{flushright}
{\textbf{Lokesh Nalla}}
\end{flushright}