\vspace{-2.5cm}
\section*{PUBLICATIONS IN REFEREED JOURNALS}
%
\begin{enumerate}
%
\item N. Lokesh and Mahesh K. Mishra, "Design of a Decoupled Sliding Mode Control for Four-Leg Distribution Static Compensator," \textit{IEEE Transactions on Power Delivery}, vol. 37, no. 6, pp. 5014-5024, Dec. 2022. \vspace{-1.5cm}
\item N. Lokesh, Mahesh K. Mishra and A. Ghosh, "Sliding Mode Control of a Four-Leg Dynamic Voltage Restorer in a Natural Reference Frame," \textit{IEEE Journal of Emerging and Selected Topics in Industrial Electronics}, vol. 4, no. 3, pp. 919-927, July 2023. 
%
\end{enumerate}
%
\vspace{-3.5cm}
\section*{PUBLICATIONS IN REFEREED CONFERENCES}
%
\begin{enumerate}
%
\item N. Lokesh, Mahesh K. Mishra and N.M.Ismail, ``Variable Structure Control for Three phase-Three Wire Nine Switch Converter with LCL Filter,'' \textit{2019 IEEE 13th International Conference on Power Electronics and Drive Systems (PEDS)}, Toulouse, France, 2019, pp. 1-5. \vspace{-1.5cm}
%
\item N. Lokesh and Mahesh K. Mishra, ``A Robust Control Scheme for an Integrated Nine-Switch Power Quality Conditioner,'' \textit{2019 National Power Electronics Conference (NPEC)}, Tiruchirappalli, India, 2019, pp. 1-6. \vspace{-1.5cm}
%
\item N. Lokesh and Mahesh K. Mishra, ``A Comparative Performance Study of Advanced PLLs for Grid Synchronization,'' \textit{2020 IEEE International Conference on Power Electronics, Smart Grid and Renewable Energy (PESGRE’2020)}, Cochin, India, 2020, pp. 1-6.  %\vspace{-0.65cm}
%
%\item Hariharan R and Mahesh K. Mishra, ``An Improved Synchronverter Control for DERs Under Grid Voltage Variations,'' \textit{IEEE Conference on Smart Technologies for Power, Energy and Control (STPEC)}, Bilaspur, India, Dec. 2021.
%
\end{enumerate}
\vspace{4.5cm}
